Enforced Invariant Confluence

### 2018-02-20 doc/paper_redux/sufficient_conditions.tex
Added a slightly less silly example.

>>>>

\todo{Write this up in full.}
Imagine we are building a system to group students together. We have a relation
of (student id, grade) and a map (group id -> set of student ids). We want to
enforce the invariant that every student in every group is in the same grade.
If we start off with an initially empty mapping, then there are conflicts. If
we start off with at least one student mapped into each group, then there are
not any conflicts.
